The first high-redshift changing-look quasars

### 2020-06-12 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
CIV_CLQs_rv1 virial mass update

\subsection{\civ\ Emission Line Evolution}
We analyse the multi-epoch spectra of the three quasars using the
QSFit spectral fitting package \citep{Calderone2017}.  One advantage
of using QSFit is that it allows constraints on the slope and
luminosity of the broad band continuum of the source. The relevant
estimated quantities, including continuum luminosity and slope at
rest-frame 1450\AA, \civ\ line luminosity, FWHM, and EW are given in
Table~\ref{tab:QSFit-results}.  {\bf All fits are obtained by taking
the Milky Way extinction \citep{Schlafly2011} into account.  The
extinction values are: $E(B-V) =0.013$ for J1205+3422; $E(B-V) =0.034$
for J1638+2827 and $E(B-V) =0.041$ for J2228+2201.  as taken from the
\href{http://ned.ipac.caltech.edu/}{NASA/IPAC Extragalactic Database} 
}. The best fit models in the region of the \civ\ emission line are
shown in Figure~\ref{fig:QSFit-CIV}.

All \civ\ lines are fitted with a single, broad, Lorentzian profile.
This allows us to account for the central peak of the \civ\ line.  No
additional narrow components are considered for several reasons.
First, in the epochs of highest brightness, such a ``narrow''
component would have FWHM $\sim$ 2000-3000~km~s$^{-1}$, i.e. values
exceeding the usual widths of genuine narrow lines ($\lesssim
1000$~km~s$^{-1}$). Second, allowing a second component to have such
large widths would make that component highly degenerate with the
``broad'' components, causing the latter to have much larger widths,
$\sim 10,000$~km~s$^{-1}$.  Finally, neglecting such a narrow
component ensures a consistent model across all epochs.

@@

\subsection{Virial Black Hole Masses}
\label{sec:BH_masses} 
The FWHMs of quasar broad lines are related to the mass of the SMBH
powering the quasar phenomenon, and that mass is assumed to be
constant on any human timescale.  Hence it is instructive to check
whether the virial products, which are the basic quantity used to
calculate single-epoch black hole mass estimates, show any
variation. This approach assumes that the broad-line region (BLR) is
virialized \citep[e.g.][]{Shen2011, Calderone2017}. The continuum
luminosity provides a proxy for the BLR radius, and the broad-line
width (FWHM) provides a proxy for the virial velocity.  This ``virial
mass'' estimate is then expressed as:
{\bf
\begin{equation}
    \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}. 
\end{equation}
\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as 0.660, 
which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
\citet{Kozlowski2017} calculate $\gamma=0.53$ and the offset as 0.64. 
\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
$z>1.3$ quasars that show significant lag measurements,
and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
their highest-confidence objects. }

The virial product for the \civ\ 
CLQs is reported in the last column of Table~\ref{tab:QSFit-results}.
{\bf Here, since our purpose is to check if this measurement varies significantly
across epochs, we use $\gamma=0.5$ as the power-law slope and
are not directly concerned with the offset.
%%
 The quoted uncertainties account only for the propagation of uncertainties in the continuum luminosities and line widths.  However, typical uncertainties associated to single epoch virial mass are $\sim$~0.5 dex, hence} implying that the virial products for our three
high-redshift CLQs are all remarkably constant and compatible with
single black hole masses per source, even in those cases where the
\civ\ estimates were deemed potentially unreliable. The object showing
the largest variation is J2228+2201, though even that source only
spans a range of 0.48~dex.

\citet{Shen2011} and \citet{Kozlowski2017} report virial black hole
masses based on \mgii\ and \civ\ for the SDSS/BOSS observations of our
targets. For J1205+3422, \citet{Shen2011} report $\log (M_{\rm BH,
MgII}/M_{\odot}) = 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot})
= 9.49 \pm 0.04$. We use the mean of five values --- three from our
three epochs and two from \citet{Shen2011} --- to calculate an adopted
SMBH mass of $\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.
J1638+2827 also has two virial mass measurements from
\citet{Shen2011}, as well as two measurements from
\citet{Kozlowski2017}. The mean mass measurement adopted for
J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot} = 9.09$. For J2228+2201,
there are two \citet{Kozlowski2017} measurements, leading to a mean
adopted mass of $\log(M_{\rm BH, vir}/M_{\odot} = 9.37$. We use these
mean SMBH masses when calculating the Eddington ratios.

@@

\begin{table}
  \centering
  \begin{tabular}{l l  cc    l     r}
    \hline
    \hline
\multirow{2}{*}{Object} & \multirow{2}{*}{MJD} & $\log (M/M_{\odot})$ &  $\log (M/M_{\odot})$ & log($L_{\rm bol}$) &  \multirow{2}{*}{$\eta_{\rm Edd}$}  \\
                                    &                                  &    QSFit                     &   Liter. value                &                             &    \\
    \hline
                                    & 53498                        &    9.39                      &  9.49$\pm$0.04$^{\dagger}$   &   47.22                  &  $-$0.61   \\
 J1205+3422               & 58538                         &    9.78                     &   ---                                        &  46.07                  &   $-$1.76 \\  %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
                                    & 58693                        &    9.39                      &                                                 &  46.57                &  $-$1.26  \\                    
    \hline 
                                    & 54553                        &   8.84                      &  8.74$\pm$0.15$\dagger$                     & 46.17   & $-$1.03  \\
J1638+2827                 & 55832                       &    8.80                             &    9.13                                         & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
                                    & 58583                        &   9.01                               &                          & 46.50   & $-$0.69   \\
    \hline 
                                     & 56189                       & 8.70                                & 8.73                         & 46.23  &  $-$1.24 \\
J2228+2201                 & 56960                       &   9.39                                &                         & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
                                     & 58693                      &  8.97                                &                         & 46.83   &  $-$0.64 \\
    \hline
    \hline
  \end{tabular}
  \caption{Virial Mass estimates, bolometric luminosities and Eddington ratios for the
    three quasars. 
    $\dagger$From \citet{Shen2011} SDSS DR7 Quasar catalog.
    $\dagger$From \citet{Shen2011} SDSS DR7 Quasar catalog.
    are given in either \citet{Shen2011} or
    \citet{Kozlowski2017} for the three CLQs. We scale these values using
    our measured $\nu L_{\nu}$ continuum luminosity values.  From
    Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.726$ for J1205+3422; $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.091$ for J1638+2827, and $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.366$ for J2228+2201.  The Eddington luminosity
    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}

>>>>

\subsection{\civ\ Emission Line Evolution}
We analyse the multi-epoch spectra of the three quasars using the
QSFit spectral fitting package \citep{Calderone2017}.  One advantage
of using QSFit is that it allows constraints on the slope and
luminosity of the broad band continuum of the source. The relevant
estimated quantities, including continuum luminosity and slope at
rest-frame 1450\AA, \civ\ line luminosity, FWHM, and EW are given in
Table~\ref{tab:QSFit-results}.  {\bf All fits are obtained by taking
the Milky Way extinction \citep{Schlafly2011} into account.  The
extinction values are: $E(B-V) =0.013$ for J1205+3422; $E(B-V) =0.034$
for J1638+2827 and $E(B-V) =0.041$ for J2228+2201, as taken from the
\href{http://ned.ipac.caltech.edu/}{NASA/IPAC Extragalactic Database} 
}. The best fit models in the region of the \civ\ emission line are
shown in Figure~\ref{fig:QSFit-CIV}.

All \civ\ lines are fitted with a single, broad, Lorentzian profile.
This allows us to account for the central peak of the \civ\ line.  No
additional narrow components are considered for several reasons.
First, in the epochs of highest brightness, such a ``narrow''
component would have FWHM $\sim$ 2000-3000~km~s$^{-1}$, i.e. values
exceeding the usual widths of genuine narrow lines ($\lesssim
1000$~km~s$^{-1}$). Second, allowing a second component to have such
large widths would make that component highly degenerate with the
``broad'' components, causing the latter to have much larger widths,
$\sim$10,000~km~s$^{-1}$.  Finally, neglecting such a narrow
component ensures a consistent model across all epochs.

@@

\subsection{Virial Black Hole Masses}
\label{sec:BH_masses} 
The FWHMs of quasar broad lines are related to the mass of the SMBH
powering the quasar phenomenon, and that mass is assumed to be
constant on any human timescale.  Hence it is instructive to check
whether the virial products, which are the basic quantity used to
calculate single-epoch black hole mass estimates, show any
variation.

This approach assumes that the broad-line region (BLR) is
virialized \citep[e.g.][]{Shen2011, Calderone2017}.
{\bf However, the \civ\ line in particular for the broad emission lines is
observed to have
line asymmetry due to outflows \citep[e.g.,][]{Gaskell1982}, 
very strong blueshifts \citep[as mentioned in the Introduction, see ][]{Richards2011},
and a component of the line profile that does not reverberate \citep[][]{Denney2012}
blurring the picture of the BH mass estimation.
With these key cavaets in mind, we acknowledge the black hole mass estimates
will have a large error, likely $\sim$0.5 dex.
}
The continuum
luminosity provides a proxy for the BLR radius, and the broad-line
width (FWHM) provides a proxy for the virial velocity.  This ``virial
mass'' estimate is then expressed as:
{\bf
\begin{equation}
%  \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}.
  \log \left( \frac{M_{\rm BH}}{M_{\odot}} \right)  = a + \log  \left[ \; \left(  \frac{L_{1450}} {10^{44} \; {\rm erg \; s^{-1}}}\right)^{\gamma} \, \right] + 2 \log \left( \frac{\rm {FWHM}}{{\rm km\; s^{-1}}} \right)
  \label{eqn:virial_masses}
\end{equation}
\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as $a=0.660$, 
which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
both the DR7 Quasar catalog and DR12 Quasar catalog.
\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
$z>1.3$ quasars that show significant lag measurements,
and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
their highest-confidence objects. }

We report a virial product for the \civ\ CLQs in the last column of
Table~\ref{tab:QSFit-results}.  {\bf Since our purpose is to check if
this measurement varies significantly across epochs, here we use
$\gamma=0.5$ as the power-law slope and are not directly concerned
with the offset.
%%
 The quoted uncertainties account only for the propagation of uncertainties in the continuum luminosities and line widths.  However, typical uncertainties associated to single epoch virial mass are $\sim$~0.5 dex, hence} implying that the virial products for our three
high-redshift CLQs are all remarkably constant and compatible with
single black hole masses per source, even in those cases where the
\civ\ estimates were deemed potentially unreliable. The object showing
the largest variation is J2228+2201, with the BH mass estimate spanning a range of 0.66~dex.

{\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ Virial masses 
calculated using equation~\ref{eqn:virial_masses}, the measured luminosites
and FWHM from QSFit and the \citet{VestergaardPeterson2006} calibrations.
}
 %%
\citet{Shen2011} and \citet{Kozlowski2017} report virial black hole
masses based on \mgii\ and \civ\ for the SDSS/BOSS observations of our
targets. For J1205+3422, \citet{Shen2011} report $\log (M_{\rm BH,
MgII}/M_{\odot}) = 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot})
= 9.49 \pm 0.04$. We use the mean of five values --- three from our
three epochs and two from \citet{Shen2011} --- to calculate an adopted
SMBH mass of $\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.
J1638+2827 also has two virial mass measurements from
\citet{Shen2011}, as well as two measurements from
\citet{Kozlowski2017}. The mean mass measurement adopted for
J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot} = 9.09$. For J2228+2201,
there are two \citet{Kozlowski2017} measurements, leading to a mean
adopted mass of $\log(M_{\rm BH, vir}/M_{\odot} = 9.37$. We use these
mean SMBH masses when calculating the Eddington ratios.

@@

\begin{table}
  \centering
  \begin{tabular}{l l  cc    l     r}
    \hline
    \hline
\multirow{2}{*}{Object} & \multirow{2}{*}{MJD} & \multicolumn{2}{c}{$\log (M/M_{\odot})$} & log($L_{\rm bol}$) &  \multirow{2}{*}{$\eta_{\rm Edd}$}  \\
                                    &                                  &    QSFit               &   Liter. value               &                             &    \\
    \hline
                                    & 53498                        &    9.39                &  9.49$\pm$0.04$^{\dagger}$   &   47.22                  &  $-$0.61   \\
 J1205+3422               & 58538                         &    9.78               &   ---                                        &  46.07                  &   $-$1.76 \\  %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
                                    & 58693                        &    9.38               &   ---                                               &  46.57                &  $-$1.26  \\                    
    \hline 
                                    & 54553                        &   8.84                &  8.74$\pm$0.15$\dagger$                     & 46.17   & $-$1.03  \\
J1638+2827                 & 55832                       &    8.80                &    9.13$^{\ddagger}$                                         & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
                                    & 58583                        &   9.01                &  ---                         & 46.50   & $-$0.69   \\
    \hline 
                                     & 56189                       & 8.70                 & 8.73$^{\ddagger}$                         & 46.23  &  $-$1.24 \\
J2228+2201                 & 56960                       &  9.39                &   ---                       & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
                                     & 58693                      &  8.97                    &    ---                      & 46.83   &  $-$0.64 \\
    \hline
    \hline
  \end{tabular}
  \caption{Virial Mass estimates, bolometric luminosities and Eddington ratios for the
    three quasars. 
    $\dagger$From the \citet{Shen2011} SDSS DR7 Quasar catalog.
    $\ddagger$From the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
%    are given in either \citet{Shen2011} or    \citet{Kozlowski2017} for the three CLQs.
    We scale these values using
    our measured $\nu L_{\nu}$ continuum luminosity values.  From
    Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.726$ for J1205+3422; $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.091$ for J1638+2827, and $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.366$ for J2228+2201.  The Eddington luminosity
    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}
